---
title: "Stats in R Assignment"
author: "Alex Lucchesi"
date: "2023/05/30"
output: html_document
---

## Assignment

For today's assignment, you will be given a blank notebook and a link to the [Call of Duty Dataset](https://www.kaggle.com/datasets/beridzeg45/call-of-duty-reviews) You will need to fill out the notebook and create your own code chunks to run code. Remember that we use this code without any quotation marks to create a code chunk: '`{r} '` \### Your Goal:

To receive credit for today's assignment, you will need to:

-   Import the dataset

```{r}
data <- read.csv("C:\\Users\\ALIYA\\OneDrive\\Documents\\Coding_Temple\\Week 6\\Call of Duty Reviews.csv")

```

-   Load the dataset into a tibble

```{r}
# Load the tidyverse package for data manipulation
library(tidyverse)

# Read the CSV file into a tibble
my_tibble <- read_csv("C:\\Users\\ALIYA\\OneDrive\\Documents\\Coding_Temple\\Week 6\\Call of Duty Reviews.csv"))
```

-   Mutate a new column

```{r}
# Load the dplyr package
library(dplyr)

# Assuming you have a tibble named my_tibble
my_tibble <- my_tibble %>%
  mutate(Combined_Column = paste("Game Title:", `Game Title`, "Platform:", Platform, "Release Year:", `Release Year`, "Publisher:", Publisher, "Metascore:", Metascore, "Critic Reviews:", `Critic Reviews`, "User Reviews:", `User Reviews`, "Critic Compound Score:", `Critic Compound Score`, "User Compound Score:", `User Compound Score`, sep = " "))

```

-   Create a hypothesis regarding your data and communicate that hypothesis in a scientific method.

    ```{r}
    correlation_result <- cor.test(my_tibble$Metascore, my_tibble$`User Reviews`, method = "pearson")
    # Correlation coefficient
    correlation_coefficient <- correlation_result$estimate

    # P-value
    p_value <- correlation_result$p.value

    ```

-   Clean the data

```{r}
library(ggplot2)
# Create a scatter plot of Metascore vs. User Reviews
ggplot(my_tibble, aes(x = Metascore, y = `User Reviews`)) +
  geom_point() +
  labs(
    x = "Metascore",
    y = "User Reviews",
    title = "Scatter Plot of Metascore vs. User Reviews"
  )
# Create a histogram and density plot for Metascores
ggplot(my_tibble, aes(x = Metascore)) +
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  geom_density(alpha = 0.5, fill = "red") +
  labs(
    x = "Metascore",
    y = "Frequency/Density",
    title = "Distribution of Metascores"
  )


```
