Hypothesis 1: Relationship between Thyroid Function and Age/Sex
There might be a relationship between thyroid function and age/sex. Thyroid-related parameters such as TSH (Thyroid Stimulating Hormone), T3 (Triiodothyronine), TT4 (Total Thyroxine), FTI (Free Thyroxine Index), and others could potentially vary based on age and sex. This hypothesis could involve analyzing the distribution of thyroid-related parameters among different age groups and genders to understand if there are any trends or patterns.

Hypothesis 2: Effect of Pregnancy on Thyroid Function
Pregnancy might have an impact on thyroid function. The data includes a "pregnant" column, and it would be interesting to explore how thyroid-related parameters change in pregnant individuals compared to those who are not pregnant. This could involve comparing TSH, T3, TT4, and FTI levels between pregnant and non-pregnant individuals to see if there is a significant difference.

```{r}
# Replace "your_file_path.csv" with the actual path to your CSV file
data <- read.csv("C:\\Users\\ALIYA\\OneDrive\\Documents\\Coding_Temple\\Week 8\\Capstone_1\\thyroidDF.csv")

# Now the data from the CSV file is stored in the 'data' variable

```

```{r}
# Clean column names
colnames(data_clean) <- gsub("[^A-Za-z0-9_]", "_", tolower(colnames(data_clean)))

# Print the cleaned column names
print(colnames(data_clean))

```


```{r}
# Remove rows with any missing values
data_clean <- na.omit(data)


```
```{r}
# Display the first 6 rows of the cleaned data
head(data_clean)

```
```{r}
# Load required library for visualization (ggplot2)
library(ggplot2)

# Perform exploratory data analysis
# Let's assume 'TSH' is a thyroid-related parameter and 'age' is the age column
# We will use box plots to visualize the distribution of TSH levels across different age groups and sexes

# Convert sex column to factor for better visualization
data_clean$sex <- factor(data_clean$sex, levels = c("F", "M"))

# Create a box plot
ggplot(data_clean, aes(x = age, y = TSH, fill = sex)) +
  geom_boxplot() +
  labs(title = "Thyroid Function by Age and Sex", x = "Age", y = "TSH Level") +
  scale_fill_discrete(name = "Sex") +
  theme_minimal()

```


```


```{r}
write.csv(data_clean, "cleaned_data.csv", row.names = FALSE)

```

